---
title: "math250_nov5_Soupafied"
author: "Josmar Osorio"
format: html
embed-resources: true
---

## Inference Problems

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(ISLR2)
```

We will be using the `Carseats` dataset from the `ISLR2` package for the following problems.
```{r}
glimpse(Carseats)
```

## Problem 1

The company claims that the average price of their Carseats is 110. We will test this claim.

**Null Hypothesis**: ($\mu = 110$)

**Alternative hypothesis**: ($\mu \ne 110$)


```{r}
t.test(Carseats$Price,
       mu = 110)
```

With a `p-value` of 1.429e-06 we overwhelmingly reject the null hypothesis. This means we reject the claim that the true mean price of the carseats is 110, and that the company is wrong.

```{r}
#| message: false
ggplot(Carseats, aes(x = Price)) +
  geom_histogram(fill = "salmon") +
  geom_vline(xintercept = 113.4677) +
  geom_vline(xintercept = 118.1223) +
  geom_vline(xintercept = 110, color = "blue") +
  scale_x_continuous(breaks = seq(0, 200, by = 10)) +
  theme_minimal()+
  labs(
    title = "Carseat Price Distribution with claimed mean and Confidence Interval",
    caption = "95% confidence interval is between the black lines and the claimed price mean is the blue line",
    y = "Count"
    
  )
```

From the plot it is clear that 110 is not between where we think the true mean is. We cannot accept the claim that the average price is 110.

## Problem 2

We will now compute a 90% confidence interval for the mean competitor price in the population.

```{r}
t.test(Carseats$CompPrice, conf.level = 0.90)
```

We are 95% confident that the true `compPrice` mean lies between 123.7109 and 126.2391.

```{r}
compPrice_m <- mean(Carseats$CompPrice)
compPrice_m
```
**Sample Mean**:

$\bar{x} = 124.975$

```{r}
MOE <- (126.2391-123.7109)/2
MOE
```

**Margin Of Error**:

$ME = \pm 1.2641$

**Confidence Interval**:

$CI = 124.975 \pm 1.2641$

## Problem 3

For this problem we will be using the `penguins` data set to create a contingency table of the `species`, `island` and marginal counts.

```{r}
t <- table(penguins$species,penguins$island)

addmargins(t)
```

## Problem 4

Upload to Github